---
title: "Ex_data_plotting assignment"
author: "Hosub Park"
date: "Apr 28, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Overview of data description
Measurements of electric power consumption in one household with a one-minute sampling rate over a period of almost 4 years. Different electrical quantities and some sub-metering values are available.
The following descriptions of the 9 variables in the dataset are taken from the UCI web site:
 * Date: Date in format dd/mm/yyyy
 * Time: time in format hh:mm:ss
 * Global_active_power: household global minute-averaged active power (in kilowatt)
 * Global_reactive_power: household global minute-averaged reactive power (in kilowatt)
 * Voltage: minute-averaged voltage (in volt)
 * Global_intensity: household global minute-averaged current intensity (in ampere)
 * Sub_metering_1: energy sub-metering No. 1 (in watt-hour of active energy). It corresponds to the kitchen, containing mainly a dishwasher, an oven and a microwave (hot plates are not electric but gas powered).
 * Sub_metering_2: energy sub-metering No. 2 (in watt-hour of active energy). It corresponds to the laundry room, containing a washing-machine, a tumble-drier, a refrigerator and a light.
 * Sub_metering_3: energy sub-metering No. 3 (in watt-hour of active energy). It corresponds to an electric water-heater and an air-conditioner.


##Find location of data to extract
This codes are just for the record. To reproduce plotting, start from next chunk.
raw data file is placed in working directory
```{r}
#read raw data
previewdb <- read.table(file="household_power_consumption.txt",nrows=100)
head(previewdb)
#This data has header, use ";" as seperator, "?" as NA

#find location
readDB <- read.table(file="household_power_consumption.txt", header=T, sep=";", na.string="?")
head(unique(readDB[,1]),20)#investigate data format of 'Date'

start_row <- head(which(readDB[,1]=="1/2/2007"), 1) #row number of start of data interested
last_row <- tail(which(readDB[,1]=="2/2/2007"), 1) #row number of end of data interested
```
```{r}
start_row
last_row
```

#For plotting data, Start from here.
##extract data & processing Date and Time
```{r}
start_row <- 66637; last_row <- 69516 #these numbers are from previous chunk.
header_db <- read.table(file="household_power_consumption.txt", header=F, sep=";", na.string="?", stringsAsFactors=FALSE, nrow=1)
ext_db <- read.table(file="household_power_consumption.txt", header=F, sep=";", na.string="?", stringsAsFactors=FALSE, skip=start_row, nrows=last_row-start_row+1)

#put header
ext_data <- ext_db 
colnames(ext_data) <- header_db

#processing Date and Time
datetime <- strptime(paste(ext_data$Date, ext_data$Time, sep=" "), format="%d/%m/%Y %T", tz = "UTC") #make Date and Time as posixlt
wdays <- strftime(datetime, format="%A")
proc_data <- cbind(datetime, wdays, ext_data) 
```
##Plot 1
```{r}
png(filename = "plot1.png", width = 480, height = 480)
hist(proc_data$Global_active_power, xlab="Global active power(kilowatts)", main="Global active power", col="red")
dev.off()
```

##Plot2
```{r}
png(filename = "plot2.png", width = 480, height = 480)
plot(proc_data$Global_active_power~proc_data$datetime, type="l", ylab="Global active power(kilowatts)")
dev.off()
```

##Plot3
```{r}
png(filename = "plot3.png", width = 480, height = 480)
plot(proc_data$Sub_metering_1~proc_data$datetime, type="l", ylab="Energy sub metering")
lines(proc_data$Sub_metering_2~proc_data$datetime, col="red")
lines(proc_data$Sub_metering_3~proc_data$datetime, col="blue")
legend("topright",col=c("black","red","blue"), lty=c(1,1,1), legend=c("Sub_metering_1","Sub_metering_2","Sub_metering_3"))
dev.off()
```

##Plot4
```{r}
png(filename = "plot4.png", width = 480, height = 480)

par(mfrow=c(2,2)) #setting multiplot

plot(proc_data$Global_active_power~proc_data$datetime, type="l", ylab="Global active power(kilowatts)")#location(1,1)

plot(proc_data$Voltage~proc_data$datetime, type="l", xlab="datetime", ylab="Voltage")#location(1,2)

plot(proc_data$Sub_metering_1~proc_data$datetime, type="l", ylab="Energy sub metering")#location(2,1)
lines(proc_data$Sub_metering_2~proc_data$datetime, col="red")
lines(proc_data$Sub_metering_3~proc_data$datetime, col="blue")
legend("topright",col=c("black","red","blue"), lty=c(1,1,1), legend=c("Sub_metering_1","Sub_metering_2","Sub_metering_3"))

plot(proc_data$Global_reactive_power~proc_data$datetime, type="h", xlab="datetime", ylab="Global_reactive_power") #location(2,2)
par(mfrow=c(1,1)) #reset multiplot setting
dev.off()
```